---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SepstratifieR

<!-- badges: start -->
<!-- badges: end -->

The goal of SepstratifieR is to stratifying patients with suspected infection into groups with different molecular characteristics. This is done based on the expression level of 7 genes measured from whole blood.

License: MIT + file LICENSE

## Installation

You can install the development version of SepstratifieR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jknightlab/SepstratifieR")
```

## Example
This is a basic example which shows you how to use this package to stratify a small set of patients into sepsis reponse groups:

```{r example}
# Load package
library(SepstratifieR)

# Load test data set
data(test_data)

# Stratify patients
predictions <- stratifyPatients(test_data)
```

```{r example_output}
predictions
```

